A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-17 paper/paper.tex

Secondly, in the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data from the newest survey period release. Thus, the 1990 prices might not be relevant anymore for the future context. Hence, we keep it as the original value to allow the users to treat it as their needs.

It is also worth noting that the treatment of unlikely wages differ in the refreshed data. In the original data by Singer and Willett (2003), wages greater than \$75 are set to be missing. However, in recent context, this value is too low to be set as the maximum threshold. We opted to use the weights from a robust linear regression to determine what should be regarded as outliers and imputed them with their predicted values as as described in Section \ref{censor}.

>>>>

Secondly, in the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data added to and released from the survey. Instead we have provided a function in the R package, \texttt{yowie}, for users to conduct the inflation adjustment when they are ready to analyse the data.

It is important to note that the treatment of unlikely wages differs in the refreshed data. In the original data by Singer and Willett (2003), wages greater than \$75 are set to be missing. However, this value is too low to be set as the maximum threshold, and it doesn't take into account temporal neighbors for an individual. We opted to use the weights from a robust linear regression to determine what should be regarded as extreme and imputed them with their predicted values as as described in Section \ref{censor}.
